Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-07 Paper.Rmd
Now, I could knit makefile upto this : But still don't know how to deal with duplicate row indexing...so commented out

Our model with environmental effects which differed in the
two tails produced simulated ecological variables with visually apparent asymmetry 
of tail dependence and non-N copula structure (Fig. \ref{fig_ms_asym_b_0.1}).
Model selection results (Table \ref{SM-tab_summary_stat_asym_sens}) and
our nonparametric statistics (Tables \ref{SM-tab_stat_npa_asym_1} -\ref{SM-tab_stat_npa_asym_2}) 
statistically confirmed the visual result.
We repeated our analyses with $b=-0.1, 0.9, -0.9$, with similar conclusions
in all cases.
<!--***DAN: Right Shya? I have written this, but I want you to show me these results
(without putting them in the paper) to make sure the statement is accurate.
But we should put the figs in the sup mat, not the stats results, I think, but we could put the figs. Or maybe we do want to put the stats. Let's look at them anyway. Maybe the sentence needs to
be rewritten if the results for other b are actually different.-->

>>>>

Our model with environmental effects which differed in the
two tails produced simulated ecological variables with visually apparent asymmetry 
of tail dependence and non-N copula structure (Fig. \ref{fig_ms_asym_b_0.1}).
Model selection results (Table \ref{SM-tab_summary_stat_asym_sens}) and
our nonparametric statistics (Tables \ref{SM-tab_stat_npa_asym}) 
statistically confirmed the visual result.
We repeated our analyses with $b=-0.1, 0.9, -0.9$, with similar conclusions
in all cases.
<!--***DAN: Right Shya? I have written this, but I want you to show me these results
(without putting them in the paper) to make sure the statement is accurate.
But we should put the figs in the sup mat, not the stats results, I think, but we could put the figs. Or maybe we do want to put the stats. Let's look at them anyway. Maybe the sentence needs to
be rewritten if the results for other b are actually different.-->

### 2019-02-07 SupportingInformation.Rmd
Now, I could knit makefile upto this : But still don't know how to deal with duplicate row indexing...so commented out

tab_asym<-readRDS("./Results/asym_sens_results/stat_npa_asym_b_0.1_b_0.9.RDS")
tab_stat_npa_asym<-c()
for(i in c(1:8)){
  temp<-make_table_stat_fn(data=tab_asym[[i]])
  tab_stat_npa_asym<-rbind(tab_stat_npa_asym,temp)
}

knitr::kable(tab_stat_npa_asym, booktabs = T, longtable=T,
             format = "latex",linesep = "",escape=F,
             caption.short = "Results for tests of whether asymmetry of tail dependence was significant
                              compared to a normal-copula null hypothesis.",
             caption ="A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more)
                      than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ 
                      or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail         
                      dependence.\\label{tab_stat_npa_asym}")%>%
             kable_styling()%>%
             group_rows("b=0.1, g$_{1}$", 2,4, escape=F) %>%
             group_rows("b=0.1, g$_{2}$", 5,7, escape=F) %>%
             group_rows("b=-0.1, g$_{1}$", 8,10, escape=F) %>%
             group_rows("b=-0.1, g$_{2}$", 11,13, escape=F) %>%
             group_rows("b=0.9, g$_{1}$", 14,16, escape=F) %>%
             group_rows("b=0.9, g$_{2}$", 17,19, escape=F) %>%
             group_rows("b=-0.9, g$_{1}$", 20,22, escape=F) %>%
             group_rows("b=-0.9, g$_{2}$", 23,25, escape=F)
```

>>>>

tab_asym<-readRDS("./Results/asym_sens_results/stat_npa_asym_b_0.1_b_0.9.RDS")
tab_stat_npa_asym<-c()
for(i in c(1:8)){
  temp<-make_table_stat_fn(data=tab_asym[[i]])
  tab_stat_npa_asym<-rbind(tab_stat_npa_asym,temp)
}
gtext<-c("b=0.1, g$_{1}$","b=0.1, g$_{2}$","b=-0.1, g$_{1}$","b=-0.1, g$_{2}$","b=0.9, g$_{1}$","b=0.9, g$_{2}$","b=-0.9, g$_{1}$","b=-0.9, g$_{2}$")
knitr::kable(tab_stat_npa_asym, booktabs = T, longtable=T,
             format = "latex",linesep = "",escape=F,
             caption.short = "Results for tests of whether asymmetry of tail dependence was significant
                              compared to a normal-copula null hypothesis.",
             caption ="A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more)
                      than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ 
                      or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail         
                      dependence.\\label{tab_stat_npa_asym}")#%>%
 #            kable_styling()%>%
 #            group_rows(index=setNames(c(3,3,3,3,3,3,3,3), gtext))
 #            group_rows("b=0.1, g$_{1}$", 2,4, escape=F) %>%
 #            group_rows("b=0.1, g$_{2}$", 5,7, escape=F) %>%
 #            group_rows("b=-0.1, g$_{1}$", 8,10, escape=F) %>%
 #            group_rows("b=-0.1, g$_{2}$", 11,13, escape=F) %>%
 #            group_rows("b=0.9, g$_{1}$", 14,16, escape=F) %>%
 #            group_rows("b=0.9, g$_{2}$", 17,19, escape=F) %>%
 #            group_rows("b=-0.9, g$_{1}$", 20,22, escape=F) %>%
 #            group_rows("b=-0.9, g$_{2}$", 23,25, escape=F)
```
